Suppl. Figure 2. Differential bacterial abundance across Tissue and Luminal microbiome

### 2023-02-24 reports/02_data_preprocessing.Rmd

datasets <- map(dataset_names, ~read.csv(paste0(input_dir,.x))) %>% set_names(., dataset_names)
metadata <- read.csv(paste0("../data/", "metadata.csv"),row.names = 1)
trx <- read.csv(paste0("../data/","Raw_gene_counts_matrix.csv"),row.names = 1)

>>>>

datasets <- map(dataset_names, ~read.csv(paste0(input_dir,.x))) %>% set_names(., dataset_names)
trx <- read.csv(paste0("../data/","Raw_gene_counts_matrix.csv"),row.names = 1)

### 2023-02-24 reports/manuscript/Figure1.Rmd

```{r Load data}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

pages <- list("Total Relative Abundance"=r ,"Alfa Diversity"=div_stat, "Bacterial Communities"=bac_communities)
write.xlsx(pages, file=paste0(result_dir,"Suppl.Tbl.01",".xlsx"))
alpa_div <- set_names(div_list, c("Luminal","Tissue"))
write.xlsx(alpa_div, file=paste0(result_dir,"alpha_diversity",".xlsx"))
```

>>>>

```{r Load data}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(magick)
  library(uwot)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

pages <- list("Total Relative Abundance"=r ,"Alfa Diversity"=div_stat, "Bacterial Communities"=bac_communities)
write.xlsx(pages, file=paste0(result_dir,"Suppl.Tbl.01",".xlsx"))
alpa_div <- set_names(div_list, c("Luminal","Tissue")) %>%
  map2(., c("Luminal_gr", "Tissue_gr"), ~left_join(.x, select(metadata, ID, .y), by="ID")) %>%
  map2(., c("Luminal_gr", "Tissue_gr"), ~select(.x, ID, .y, everything()))
write.xlsx(alpa_div, file=paste0(result_dir,"alpha_diversity",".xlsx"))
```

### 2023-02-24 reports/manuscript/Figure2.Rmd

```{r Load data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

>>>>

```{r Load data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(igraph)
  library(fgsea)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

### 2023-02-24 reports/manuscript/Suppl.Figure2.Rmd

```{r Suppl.Fig.2 Diff_bact_abundance, warning=FALSE, message=FALSE, fig.width=10, fig.height=9}
# all_microbiome <- cbind(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]],
#                         datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])
# datasets <- factor(c( rep("Tissue",ncol(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]])) , rep("Luminal",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) ))
# datasets <- datasets[ colSums(all_microbiome)>0 ]
# all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

all_microbiome <- cbind(datasets_all_samples[["ASV_Tissue_normalized"]],
                        datasets_all_samples[["ASV_Luminal_normalized"]])
datasets <- factor(c( rep("Tissue",ncol(datasets_all_samples[["ASV_Tissue_normalized"]])) , rep("Luminal",ncol(datasets_all_samples[["ASV_Luminal_normalized"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

>>>>

```{r Suppl.Fig.2 Diff_bact_abundance, warning=FALSE, message=FALSE, fig.width=10, fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_Tissue_normalized"]],
                        datasets_all_samples[["ASV_Luminal_normalized"]])
datasets <- factor(c( rep("Tissue",ncol(datasets_all_samples[["ASV_Tissue_normalized"]])) , rep("Luminal",ncol(datasets_all_samples[["ASV_Luminal_normalized"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]
